Sketch Recogniton using Particle Swarm Algorithm

### 2009-04-12 draft/ChapterIntroduction.tex
after correctly splled now look at any thing else

Sketch recognition is divided into three steps: preprocessing, segmentation and symbol recognition. The preprocessing phase captures user input stroke points and collects basic information about the stroke then proceeds to remove noise and compute basic statistical and geometrical information. In the segmentation phase, the strokes are divided into a set of simple geometrical primitives or segments. In the third phase, sketch recognition, strokes and segments are clustered to formulate symbols that can be recognized by a classifier system.
There are several problems in this research area that need to be handled to implement an integrated sketch recognition system. The fact that the user draws strokes in a spontaneous and ambiguous manner that intensifies the challenges. One of the main problems is segmenting spontaneous strokes drawn by the user into geometrical primitive segments. Another major problem is the high level of ambiguities in the drawing. The next sections describe each problem in details.

@@

\section{Thesis Overview}
This thesis is arranged as follows: chapter \ref{sec:Survey} presents a survey of different components of the sketch recognition. Chapter \ref{sec:ParticleSwramOptimization} gives a review on swarm intelligance and particle swarm optimization.  Chapter \ref{sec:proposedSystem} describes the proposed system and its main building blocks. The comparative study of the different techniques and their detailed results in various experiments are given in chapter \ref{sec:Evaluation}. Finally, chapter \ref{sec:DiscussionConclusion} presents the conclusions of this thesis and suggested future work.
%This thesis is arranged such that chapter \ref{} presents a survey of different components of the sketch recognition. Chapter \ref{} describe the proposed system and its main building blocks. The details description of each component is presented in Chapter \ref{}. The comparative study of different techniques with the detailed results of various experiments are detailed in chapter\ref{}. Finally, chapter \ref{} presents the conclusions of this thesis and suggested future work.

>>>>

Sketch recognition is divided into three steps: preprocessing, segmentation and symbol recognition. The preprocessing phase captures user input stroke points and collects basic information about the stroke then proceeds to remove noise and compute basic statistical and geometrical information. In the segmentation phase, the strokes are divided into a set of simple geometrical primitives or segments. In the third phase, sketch recognition, strokes and segments are clustered to formulate symbols that can be recognized by a classifier system.
There are several problems in this research area that need to be handled to implement an integrated sketch recognition system. The fact that the user draws strokes in a spontaneous and ambiguous manner intensifies the challenges. One of the main problems is segmenting spontaneous strokes drawn by the user into geometrical primitive segments. Another major problem is the high level of ambiguities in the drawing. The next sections describe each problem in details.

@@

\section{Thesis Overview}
This thesis is arranged as follows: chapter \ref{sec:Survey} presents a survey of different components of the sketch recognition. Chapter \ref{sec:ParticleSwramOptimization} gives a review on swarm intelligence and particle swarm optimization.  Chapter \ref{sec:proposedSystem} describes the proposed system and its main building blocks. The comparative study of the different techniques and their detailed results in various experiments are given in chapter \ref{sec:Evaluation}. Finally, chapter \ref{sec:DiscussionConclusion} presents the conclusions of this thesis and suggested future work.
